\textbf{Designing a Virtual Security Layer for Cloud Content}

### 2015-11-24 tex/paper.tex
Written some basic implementation introduction

@@

\subsubsection{Reflux}
Explain difference to MVC etc.

@@

\subsubsection{REST}
REST stands for representational state transfer, it is an architectural idea for writing stateless services. These 
services usually use URIs to identify specific resources and HTTP to modify or query these resources~\cite{REST}. 
In this work we use a RESTful API, which means that it is an API following the REST architecture.

@@

\section{Background}
\subsection{About Uprise}
Uprise is a company based in Uppsala, Sweden.

@@

\newpage 
\section{Copy-on-Write}
As the persistent storage does not implement transactions or locks a lot of different problems can occur when several 
clients are working on the same data set at the same time. Such problems could be race conditions and determining the 
happened-before relation. In this work this problem is solved by implementing Copy-on-Write.

@@

TODO: Insert more systems here
\section{Implementation}
\subsection{Perius}
Perius is the implementation that was done to solve the problem at hand at Uprise. This implementation is far from as 
efficient as the others in most aspects, but more efficient in some. As the implementation is built upon MongoDB as 
persistent storage and not a pure tree structure, single nodes can be fetched in O(1) but when querying for subtrees 
they need to be built first, which takes O(log(n)), where n is the number of nodes in the subtree.

>>>>

The research question that this report answers is whether it is practically feasible to use Copy-on-Write 
for a high-level system like the one that is implemented. The work also thoroughly compares different types of lazy 
snapshots to figure out which is the most

@@

\subsubsection{Reflux}
Reflux~\cite{REFLUX} is an idea and a simple library of how to structure your application. It features a unidirectional
dataflow (see Figure~\ref{fig:reflux}) which makes it more suitable, than for example Flux~\cite{FLUX}, when using a 
functional reactive programming style.

\begin{figure}[htp] 
    \centering
    \includegraphics[scale=0.4]{reflux.png}
    \caption{Reflux unidirectional dataflow}
    \label{fig:reflux}
\end{figure}

@@

\subsubsection{REST} REST stands for representational state transfer, it is an architectural 
idea for writing stateless services. These services usually use URIs to identify specific resources and HTTP to 
modify or query these resources~\cite{REST}.

In this work we use a RESTful API, which means that it is an API following the REST architecture.

@@

\section{Background}
\subsection{About Uprise}
Uprise is a company based in Uppsala, Sweden. It is an EA studio focussing on creating great gaming experiences, that means 
that they are not focussed on the actual gameplay which other EA studios like DICE is.

At the moment they are for example very involved with producing the Star Wars Battlefront game by making menu systems and 
developing the companion app, Battlefront companion.

@@

\newpage 
\section{Copy-on-Write}
\label{sec:copy-on-write}
As the persistent storage does not implement transactions or locks a lot of different problems can occur when several 
clients are working on the same data set at the same time. Such problems could be race conditions and determining the 
happened-before relation. In this work this problem is solved by implementing Copy-on-Write.

@@

TODO: Insert more systems here
\section{Implementation}
\subsection{Perius}
Perius is the implementation that was done to solve the problem at hand at Uprise. Perius has a
back-end written in Scala and a front-end written in ES6 (Javascript), but they are both interchangeable. 
The back-end has a REST API running, which is how the front-end communicates with the back-end.

TODO: Picture of the front-end

The service features a virtual file structure over the assets that has been stored, snapshots,
security management of whole containers as well as individual files, audit and access logging, multi
project support and a modular design for persistent storage.

The front-end is written in ES6 with React and Reflux, the styling is done with the help of
Bootstrap.

\subsection{Snapshots}
This implementation is far from as 
efficient as the other Copy-on-Write systems described in Section~\ref{sec:copy-on-write} in most aspects, but more efficient 
in some. As the implementation is built upon MongoDB as persistent storage and not a pure tree structure, single nodes 
can be fetched in O(1) but when querying for subtrees they need to be built first, which takes O(log(n)), where n is the 
number of nodes in the subtree.
